# Run Spatial Analysis

---
title: "borough_cleaner.rmd"
author: "Felix Bridgeman"
date: "2024-10-04"
output: html_document
---

This script imports ground truth parking data as shapefiles (either points, polylines, or polygons),
cleans them, and merges them into one clean file with which to conduct analysis.

Into ./data/clean/ this script saves the cleaned boroughs as shapefiles named [BOROUGH NAME]_clean.shp
as well as three merged files for each data type:
- joint_points_clean.shp
- joint_polygons_clean.shp
- joint_polylines_clean.shp

The cleaner also imports a shapefile of the PanoIDs of all SVIs
into an sf object called all_images, assigns them to a borough, cleans the sf object, and saves it as
"all_images_with_boroughs.shp" in the same directory.

INPUTS:
- `joint_points_clean.shp`: Cleaned shapefile containing point geometries for parking data.
- `joint_polylines_clean.shp`: Cleaned shapefile containing polyline geometries for parking data.
- `joint_polygons_clean.shp`: Cleaned shapefile containing polygon geometries for parking data.
- `all_images_with_boroughs.shp`: Shapefile of SVI PanoIDs assigned to boroughs.
- `borough_polygons.shp`: Shapefile containing the boundaries of London boroughs.
- `2024-09-15 14_44_20.478681_fileInfo.csv`: CSV file containing PanoIDs and Yale HPC filenames for ALL SVI images across London.

OUTPUTS:
- `images_near_parking.shp`: Shapefile containing images that fall within the buffer area.
- `images_outside_parking.shp`: Shapefile containing images that fall outside the buffer area.
- `near_parking_london-panoid_fileInfo-roboflow.csv`: CSV file with PanoIDs and filenames for images near parking areas.
- `outside_parking_london-panoid_fileInfo-roboflow.csv`: CSV file with PanoIDs and filenames for images outside parking areas.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lwgeom)
library(sp)
library(sf)
library(ggplot2)
#setseed(123)
```

Load shp files
```{r}
# Get working directory (should be ~/yolov8/)
getwd()

# Load borough polygons
borough_polygons <- st_read(dsn = "./data/raw/borough_polygons", layer = "london_borough_onstreet")
# Joint points
joint_points_clean <- st_read(dsn = "./data/clean/joint_points_clean.shp", layer = "joint_points_clean")
# Joint polygons
joint_polygons_clean <- st_read(dsn = "./data/clean/joint_polygons_clean.shp", layer = "joint_polygons_clean")
# Joint polylines
joint_polylines_clean <- st_read(dsn = "./data/clean/joint_polylines_clean.shp", layer = "joint_polylines_clean")


# Load all images with boroughs
all_images_with_boroughs <- st_read(dsn = "./data/clean/all_images_with_boroughs.shp", layer = "all_images_with_boroughs")

```

Import Point Data

```{r}
# create a buffer object
POINT_BUFFER_DIST = 5
POLYLINE_BUFFER_DIST = 2
POLYGON_BUFFER_DIST = 2

# create a buffer around the points
joint_points_buffer <- st_buffer(joint_points_clean, dist = POINT_BUFFER_DIST) %>%
  select(-GSS_CODE) %>%
  mutate(original_shape = "point")

# create a buffer around the polygons
joint_polygons_buffer <- st_buffer(joint_polygons_clean, dist = POLYLINE_BUFFER_DIST) %>%
  mutate(original_shape = "polygon")

# create a buffer around the polylines
joint_polylines_buffer <- st_buffer(joint_polylines_clean, dist = POLYGON_BUFFER_DIST) %>%
  mutate(original_shape = "polyline")

# inspect all buffers
head(joint_points_buffer)
head(joint_polygons_buffer)
head(joint_polylines_buffer)

# merge buffers into one sf object
all_buffers <- rbind(joint_points_buffer, joint_polygons_buffer, joint_polylines_buffer)

# calculate total area of all buffers
total_buffer_area <- sum(st_area(all_buffers))

# identify the panoids that fall inside the buffers
images_in_buffer_area <- st_within(all_images_with_boroughs, all_buffers)
points_inside_buffer_area <- lengths(images_in_buffer_area) > 0
images_in_buffer_area <- all_images_with_boroughs[points_inside_buffer_area, ]

# identify the panoids that fall inside the buffers
images_in_buffer_area <- st_within(all_images_with_boroughs, all_buffers)
points_inside_buffer_area <- lengths(images_in_buffer_area) > 0
images_in_buffer_area <- all_images_with_boroughs[points_inside_buffer_area, ]

# identify the panoids that fall outside the buffers
images_outside_buffer_area <- images_in_selected_boroughs %>%
  filter(!(panoid %in% images_in_buffer_area$panoid))



# BOROUGHS FOR SAMPLING
# - Camden
# - City of London
# - Hackney
# - Harrow
# - Islington
# - Sutton
# - Tower Hamlets
# - Wandsworth
# - Westminster

# create a df for just the selected boroughs for sampling
selected_borough_polygons <- borough_polygons %>%
  filter(NAME %in% c("Camden",
                     "City of London",
                     "Hackney",
                     "Harrow",
                     "Hounslow",
                     "Islington",
                     "Sutton",
                     "Tower Hamlets",
                     "Wandsworth",
                     "Westminster"))

# likewise create a df for just the selected INNER LONDON boroughs that are used for sampling
# images_in_inner_boroughs <- all_images_with_boroughs %>%
#   filter(borough %in% c("Camden",
#                         "Hackney",
#                         "Islington",
#                         "Westminster"))


```

# Quick analysis of the data
```{r}
# calculate total area of selected boroughs
selected_borough_area <- sum(st_area(selected_borough_polygons))

# calculate total area of all boroughs
total_borough_area <- sum(st_area(borough_polygons))

# calculate the percentage of the total area covered by the selected boroughs
selected_borough_area / total_borough_area

# calculate the percentage of the total area covered by the buffers
total_buffer_area / total_borough_area

# calculate the percentage of the total area covered by the buffers in the selected boroughs
total_buffer_area / selected_borough_area

# calculate the percentage of images that are in the selected boroughs
nrow(images_in_selected_boroughs) / nrow(all_images_with_boroughs)

# calculate the percentage of images in the buffer area out of the total area
nrow(images_in_buffer_area) / nrow(all_images_with_boroughs)

# calculate the percentage of images in the buffer area out of the selected boroughs
nrow(images_in_buffer_area) / nrow(images_in_selected_boroughs)
```

### Saving shapefiles of Images IN and OUT (and FAR OUT) of Buffer Area

```{r}
#save as shp
st_write(images_in_buffer_area, "./results/images_near_parking.shp")
st_write(images_outside_buffer_area, "./results/images_outside_parking.shp")
#st_write(images_far_outside_buffer_area, "./results/images_far_outside_parking.shp")
#st_write(inner_images_outside_buffer, "./results/innerlondon_images_outside_parking.shp")

#### SEEING AS I ALREADY SAMPLED THE IMAGES AND SAVED THAT FILE,
#### DO NOT RUN THIS SCRIPT AGAIN SO AS NOT TO OVERWRITE THE ORIGINAL SAMPLE
# set seed
set.seed(123)

# random sample of these images, n = 200
# images_in_buffer_area_sample <- images_in_buffer_area %>%
#   sample_n(200)
# images_outside_buffer_area_sample <- images_outside_buffer_area %>%
#   sample_n(200)
# images_far_outside_buffer_area_sample <- images_far_outside_buffer_area %>%
#   sample_n(200)
# inner_images_outside_buffer_sample <- inner_images_outside_buffer %>%
#   sample_n(400)

# st_write(images_in_buffer_area_sample, "./results/images_near_parking_sample200.shp")
# st_write(images_outside_buffer_area_sample, "./results/images_outside_parking_sample200.shp")
# st_write(images_far_outside_buffer_area_sample, "./results/images_far_outside_parking_sample200.shp")
# st_write(inner_images_outside_buffer_sample, "./results/innerlondon_images_outside_parking_sample400.shp")
```

### Saving the PanoIDs and Filenames of SVIs in each subset
Here we save find the PanoIDs and images for each SVI in each subset (in buffer, out of buffer) into its own CSV to be accessed for labelling and uploading to model
(Extract Panoids and Filenames)

```{r}
# This script finds the panoids paths used for labeling parked vs moving vehicles in Roboflow. 

inside_gdf <- images_in_buffer_area_sample %>%
  select(panoid)

outside_gdf <- images_outside_buffer_area_sample %>%
  select(panoid)

far_outside_gdf <- images_far_outside_buffer_area_sample %>%
  select(panoid)

innerlondon_outside_gdf <- inner_images_outside_buffer_sample %>%
  select(panoid)

# Load the CSV file
csv_path <- "./data/raw/2024-09-15 14_44_20.478681_fileInfo.csv"
csv_df <- read.csv(csv_path, stringsAsFactors = FALSE)

# Extract the 'panoid' by removing everything after the last underscore and .jpg
csv_df <- csv_df %>%
  mutate(panoid = str_extract(name, ".*(?=_)"))

# Filter the CSV data to keep only rows where the 'panoid' is present in the shapefile panoids
inside_filtered_csv_df <- csv_df %>%
  filter(panoid %in% inside_gdf$panoid)

outside_filtered_csv_df <- csv_df %>%
  filter(panoid %in% outside_gdf$panoid)

far_outside_filtered_csv_df <- csv_df %>%
  filter(panoid %in% far_outside_gdf$panoid)

innerlondon_outside_filtered_csv_df <- csv_df %>%
  filter(panoid %in% innerlondon_outside_gdf$panoid)

# Display the filtered paths that correspond to the panoids in the shapefile
inside_filtered_csv_df <- inside_filtered_csv_df %>%
  select(folder, name, type)

outside_filtered_csv_df <- outside_filtered_csv_df %>%
  select(folder, name, type)

far_outside_filtered_csv_df <- far_outside_filtered_csv_df %>%
  select(folder, name, type)

innerlondon_outside_filtered_csv_df <- innerlondon_outside_filtered_csv_df %>%
  select(folder, name, type)

# merged_filtered_csv_df <- rbind(inside_filtered_csv_df, outside_filtered_csv_df)

csv_dir <- ".data/processed/sampled_panoID_locations/CSVs/"
concatenated_csv_path <- paste0(csv_dir, "sampled_panoID_locations.csv")
inside_output_path <- paste0(csv_dir, "near_parking_london-panoid_fileInfo-roboflow.csv")
outside_output_path <- paste0(csv_dir, "outside_parking_london-panoid_fileInfo-roboflow.csv")
#far_outside_output_path <- paste0(csv_dir, "far_outside_parking_london-panoid_fileInfo-roboflow.csv")
#innerlondon_outside_output_path <- paste0(csv_dir, "innerlondon_outside_parking-panoid_fileInfo-roboflow.csv")

# merged_output_path <- paste0(csv_dir, "london-panoid_fileInfo-roboflow.csv")

write.csv(inside_filtered_csv_df, inside_output_path, row.names = FALSE)
write.csv(outside_filtered_csv_df, outside_output_path, row.names = FALSE)
# write.csv(far_outside_filtered_csv_df, far_outside_output_path, row.names = FALSE)
# write.csv(innerlondon_outside_filtered_csv_df, innerlondon_outside_output_path, row.names = FALSE)

# original_selected_panoids$panoid == inside_selected_panoids$panoid
# compare the two dataframes
# original_selected_panoids <- read.csv("./panoids/london-panoid_fileInfo-roboflow.csv")
# original_selected_panoids$panoid == inside_selected_panoids$panoid
```


### LEGACY CODE

```{r}
# images_in_inner_boroughs <- all_images_with_boroughs %>%
#   filter(borough %in% c("Camden",
#                         "Hackney",
#                         "Islington",
#                         "Westminster"))

# # identify the panoids that fall inside the buffers
# images_in_buffer_area <- st_within(all_images_with_boroughs, all_buffers)
# points_inside_buffer_area <- lengths(images_in_buffer_area) > 0
# images_in_buffer_area <- all_images_with_boroughs[points_inside_buffer_area, ]

# # identify the panoids that fall outside the buffers
# images_outside_buffer_area <- images_in_selected_boroughs %>%
#   filter(!(panoid %in% images_in_buffer_area$panoid))

# inner_images_outside_buffer <- images_outside_buffer_area %>%
#   filter(borough %in% c("Camden",
#                         "Hackney",
#                         "Islington",
#                         "Westminster"))
  
# # create a buffer around the points
# joint_points_buffer2 <- st_buffer(joint_points_clean, dist = 10) %>%
#   select(-GSS_CODE) %>%
#   mutate(original_shape = "point")

# # create a buffer around the polygons
# joint_polygons_buffer2 <- st_buffer(joint_polygons_clean, dist = 10) %>%
#   mutate(original_shape = "polygon")

# # create a buffer around the polylines
# joint_polylines_buffer2 <- st_buffer(joint_polylines_clean, dist = 10) %>%
#   mutate(original_shape = "polyline")

# all_buffers2 <- rbind(joint_points_buffer2, joint_polygons_buffer2, joint_polylines_buffer2)

# # identify panoids that fall far from buffers
# inside_not_far <- st_within(images_in_selected_boroughs, all_buffers2)
# points_not_far <- lengths(inside_not_far) > 0
# images_far_outside_buffer_area <- images_in_selected_boroughs[!points_not_far, ]

# # calculate the percentage of images that are in the selected boroughs
# nrow(images_in_selected_boroughs) / nrow(all_images_with_boroughs)

# # calculate the percentage of images in the buffer area out of the total area
# nrow(images_in_buffer_area) / nrow(all_images_with_boroughs)

# # calculate the percentage of images in the buffer area out of the selected boroughs
# nrow(images_in_buffer_area) / nrow(images_in_selected_boroughs)

# calculate percentage of images that were in buffer area by borough
# first create a borough df
test_boroughs <- c("Camden",
              "City of London",
              "Hackney",
              "Harrow",
              "Hounslow",
              "Islington",
              "Sutton",
              "Tower Hamlets",
              "Wandsworth",
              "Westminster")

test_boroughs <- as.data.frame(test_boroughs)
# label first column NAME
colnames(test_boroughs) <- c("NAME")
#lowercase id
test_boroughs$id <- c("camden",
                        "city_of_london",
                        "hackney",
                        "harrow",
                        "hounslow",
                        "islington",
                        "sutton",
                        "tower_hamlets",
                        "wandsworth",
                        "westminster")

# now let's fill the df with its area, its images and its images in buffer
test_boroughs$area <- NA
test_boroughs$images <- NA
test_boroughs$images_in_buffer <- NA
test_boroughs$images_outside_buffer <- NA

# fill original_shape manually
test_boroughs <- test_boroughs %>%
  mutate(original_shape = case_when(
    NAME == "Camden" ~ "point",
    NAME == "City of London" ~ "polygon",
    NAME == "Hackney" ~ "polygon",
    NAME == "Harrow" ~ "polygon",
    NAME == "Hounslow" ~ "polyline",
    NAME == "Islington" ~ "polygon",
    NAME == "Sutton" ~ "polyline",
    NAME == "Tower Hamlets" ~ "polyline",
    NAME == "Wandsworth" ~ "polygon",
    NAME == "Westminster" ~ "point"
  )
  )


# Check the result
head(test_boroughs)
    
# fill the area
for (i in 1:nrow(test_boroughs)) {
  test_boroughs$area[i] <- sum(st_area(borough_polygons[borough_polygons$NAME == test_boroughs$NAME[i], ]))
}

# fill the buffer area
for (i in 1:nrow(test_boroughs)) {
  test_boroughs$buffer_area[i] <- sum(st_area(all_buffers[all_buffers$borough == test_boroughs$id[i], ]))
}

# fill the images
for (i in 1:nrow(test_boroughs)) {
  test_boroughs$images[i] <- nrow(all_images_with_boroughs[all_images_with_boroughs$borough == test_boroughs$NAME[i], ])
}

# fill the images in buffer
for (i in 1:nrow(test_boroughs)) {
  test_boroughs$images_in_buffer[i] <- nrow(images_in_buffer_area[images_in_buffer_area$borough == test_boroughs$NAME[i], ])
}

# fill the images out of buffer
for (i in 1:nrow(test_boroughs)) {
  test_boroughs$images_outside_buffer[i] <- nrow(images_outside_buffer_area[images_outside_buffer_area$borough == test_boroughs$NAME[i], ])
}

test_boroughs

test_boroughs$percentage_of_images_in_buffer <- test_boroughs$images_in_buffer / test_boroughs$images

# plot total number of images relative to borough area
test_boroughs %>%
  ggplot(aes(x = NAME,
             y = images/area,
             fill = original_shape)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(title = "Number of images relative to borough area",
       x = "Borough",
       y = "Number of images",
       fill = "Original shape")

# plot by borough
g_borough_prop <- test_boroughs %>%
  ggplot(aes(x = NAME,
                          y = images_in_buffer/images * 100,
                          fill = original_shape)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  # 0-100 axis
  scale_y_continuous(limits = c(0, 100)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(title = "Percentage of images in buffer area by borough",
       x = "Shape",
       y = "Percentage of images in buffer area (%)",
       fill = "Original shape")

# plot by original shape
g_shape_prop <-
test_boroughs %>%
  group_by(original_shape) %>%
  summarise(images_in_buffer = sum(images_in_buffer),
            images = sum(images)) %>%
  ggplot(aes(x = original_shape,
                          y = images_in_buffer/images * 100,
                          fill = original_shape)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  # 0-100 axis
  scale_y_continuous(limits = c(0, 100)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(title = "Percentage of images in buffer area by original shape type",
       x = "Shape",
       y = "Percentage of images in buffer area (%)",
       fill = "Original shape")

ggsave(g_borough_prop, width = 6, height = 4, units = "in", filename = "./img/borough_prop.png")
ggsave(g_shape_prop, width = 6, height = 4, units = "in", filename = "./img/shape_prop.png")
```

# Visualizations

```{r, fig.width = 10}
# All points, polygons and polylines on a map
g_clean_spaces <- ggplot() +
  geom_sf(data = borough_polygons, color = 'lightgrey', size = 1) +
  geom_sf(data = joint_points_clean, aes(color = borough), size = 0.0001, shape = 20) +
  geom_sf(data = joint_polygons_clean, aes(color = borough), size = 0.1) +
  geom_sf(data = joint_polylines_clean, aes(color = borough), size = 0.1) +
  theme_minimal() +
  labs(title = "All Clean On-Street Parking Data") +
  theme(legend.position = "none") +
  geom_sf_text(data = borough_polygons, aes(label = NAME), size = 1.5, nudge_y = 0.0005, nudge_x = 0.0005)

g_clean_spaces
ggsave(g_clean_spaces, width = 10, height = 7.5, units = "in", dpi = 600, filename = "./img/clean_spaces.png")
ggsave(g_clean_spaces, width = 10, height = 7.5, units = "in", dpi = 600, filename = "./img/clean_spaces.jpg")

# Plot point buffers
g_buffers <- ggplot() +
  
  # Plot the buffer polygons (joint_points_buffer)
  geom_sf(data = all_buffers, fill = "lightblue", color = "blue", alpha = 0.3)

  # Add titles and labels
  labs(
    title = "Buffer Polygons",
    x = "Longitude", y = "Latitude"
  ) +
  theme_minimal()
g_buffers

# plot which images lack borough assignments
all_images_with_boroughs %>%
  ggplot() +
  geom_sf(size = 0.01) +
  geom_sf(data = . %>% filter(is.na(borough)), color = "red", size = 0.01) +
  labs(title = "Images without boroughs") +
  theme_minimal()

# plot `images_in_buffer_area` on top of the `all_buffers`
# color `all_buffers` by `original_shape`
ggplot() +
  geom_sf(data = all_buffers,
          aes(fill = original_shape, color = original_shape),
          size = 0.1) +
  geom_sf(data = images_in_buffer_area,
          color = "red",
          size = 0.1) +
  labs(title = "Images in buffer area") +
  theme_minimal()

# plot `images_outside_buffer_area` on top of the `all_buffers`
# color `all_buffers` by `original_shape`
ggplot() +
  geom_sf(data = all_buffers,
          aes(fill = original_shape, color = original_shape),
          size = 0.1) +
  geom_sf(data = images_outside_buffer_area,
          color = "red",
          size = 0.1) +
  labs(title = "Images outside buffer area") +
  theme_minimal()

# plot `images_far_outside_buffer_area` on top of the `all_buffers`
# color `all_buffers` by `original_shape`
ggplot() +
  # basemap of London
  geom_sf(data = borough_polygons, color = 'lightgrey', size = 1) +
  # all buffers
  geom_sf(data = all_buffers,
          aes(fill = original_shape, color = original_shape),
          size = 0.1,
          alpha = 0.5) +
  # images outside buffer area
  geom_sf(data = images_far_outside_buffer_area,
          color = "red",
          size = 0.1) +
  labs(title = "Images far outside buffer area") +
  theme_minimal()

# map all images in city of london and with all selected images on top
# first map the polygon for city of london
all_images_with_boroughs %>% filter(borough == "City of London")


```

### List of Images IN and OUT and FAR OUT of Buffer Area

```{r}
#save as shp
st_write(images_in_buffer_area, "./results/images_near_parking.shp")
st_write(images_outside_buffer_area, "./results/images_outside_parking.shp")
st_write(images_far_outside_buffer_area, "./results/images_far_outside_parking.shp")
st_write(inner_images_outside_buffer, "./results/innerlondon_images_outside_parking.shp")
# set seed
set.seed(123)

# random sample of these images, n = 200
images_in_buffer_area_sample <- images_in_buffer_area %>%
  sample_n(200)
images_outside_buffer_area_sample <- images_outside_buffer_area %>%
  sample_n(200)
images_far_outside_buffer_area_sample <- images_far_outside_buffer_area %>%
  sample_n(200)

inner_images_outside_buffer_sample <- inner_images_outside_buffer %>%
  sample_n(400)

st_write(images_in_buffer_area_sample, "./results/images_near_parking_sample200.shp")
st_write(images_outside_buffer_area_sample, "./results/images_outside_parking_sample200.shp")
st_write(images_far_outside_buffer_area_sample, "./results/images_far_outside_parking_sample200.shp")
st_write(inner_images_outside_buffer_sample, "./results/innerlondon_images_outside_parking_sample400.shp")
```

### Download images

```{r}
# create the folder if it doesn't exist
# dir.create("./collected_images", showWarnings = FALSE)

# load panoids csv
# selected_panoids <- read.csv("./panoids/london-panoid_fileInfo-roboflow.csv")
# selected_panoids <- selected_panoids %>%
#   # grep delete everything before the third "/"
#   mutate(location = gsub(".*?/.*?/.*?/(.*)", "\\1", folder)) %>%
#   mutate(old_pathname = paste0("/", location, "/", name)) %>%
#   mutate(new_pathname = paste0("./collected_images/", name))
# 
# # save each image using "pathname" to a folder called "collected images" in current directory
# file.copy(selected_panoids$old_pathname, "./collected_images", overwrite = FALSE)
```


### Extract Panoids and Filenames

```{r}
# This script finds the panoids paths used for labeling parked vs moving vehicles in Roboflow. 

inside_gdf <- images_in_buffer_area_sample %>%
  select(panoid)

outside_gdf <- images_outside_buffer_area_sample %>%
  select(panoid)

far_outside_gdf <- images_far_outside_buffer_area_sample %>%
  select(panoid)

innerlondon_outside_gdf <- inner_images_outside_buffer_sample %>%
  select(panoid)

# Load the CSV file
csv_path <- "2024-09-15 14_44_20.478681_fileInfo.csv"
csv_df <- read.csv(csv_path, stringsAsFactors = FALSE)

# Extract the 'panoid' by removing everything after the last underscore and .jpg
csv_df <- csv_df %>%
  mutate(panoid = str_extract(name, ".*(?=_)"))

# Filter the CSV data to keep only rows where the 'panoid' is present in the shapefile panoids
inside_filtered_csv_df <- csv_df %>%
  filter(panoid %in% inside_gdf$panoid)

outside_filtered_csv_df <- csv_df %>%
  filter(panoid %in% outside_gdf$panoid)

far_outside_filtered_csv_df <- csv_df %>%
  filter(panoid %in% far_outside_gdf$panoid)

innerlondon_outside_filtered_csv_df <- csv_df %>%
  filter(panoid %in% innerlondon_outside_gdf$panoid)

# Display the filtered paths that correspond to the panoids in the shapefile
inside_filtered_csv_df <- inside_filtered_csv_df %>%
  select(folder, name, type)

outside_filtered_csv_df <- outside_filtered_csv_df %>%
  select(folder, name, type)

far_outside_filtered_csv_df <- far_outside_filtered_csv_df %>%
  select(folder, name, type)

innerlondon_outside_filtered_csv_df <- innerlondon_outside_filtered_csv_df %>%
  select(folder, name, type)

# merged_filtered_csv_df <- rbind(inside_filtered_csv_df, outside_filtered_csv_df)

inside_output_path <- "./results/near_parking_london-panoid_fileInfo-roboflow.csv"
outside_output_path <- "./results/outside_parking_london-panoid_fileInfo-roboflow.csv"
far_outside_output_path <- "./results/far_outside_parking_london-panoid_fileInfo-roboflow.csv"
innerlondon_outside_output_path <- "./results/innerlondon_outside_parking-panoid_fileInfo-roboflow.csv"

# merged_output_path <- "./results/london-panoid_fileInfo-roboflow.csv"

write.csv(inside_filtered_csv_df, inside_output_path, row.names = FALSE)
write.csv(outside_filtered_csv_df, outside_output_path, row.names = FALSE)
write.csv(far_outside_filtered_csv_df, far_outside_output_path, row.names = FALSE)
write.csv(innerlondon_outside_filtered_csv_df, innerlondon_outside_output_path, row.names = FALSE)

# original_selected_panoids$panoid == inside_selected_panoids$panoid
# compare the two dataframes
# original_selected_panoids <- read.csv("./panoids/london-panoid_fileInfo-roboflow.csv")
# original_selected_panoids$panoid == inside_selected_panoids$panoid
```

<!-- ### Gaining an Additional Sample of Images far From Parked Cars -->

```{r}
# images_far_outside_buffer_area_sample <- images_far_outside_buffer_area %>%
#   sample_n(300) %>%
  
``` 

## Visualisations for Report

```{r}
borough_polygons <- st_read(dsn = "../raw_london/On-street parking/On-street parking (Alex)", layer = "london_borough_onstreet")
original_boroughs = c("Camden",
                  "City of London",
                  "Hackney",
                  "Harrow",
                  "Hounslow",
                  "Islington",
                  "Kensington and Chelsea",
                  "Sutton",
                  "Tower Hamlets",
                  "Wandsworth",
                  "Westminster")
sampling_boroughs = c("Camden",
                  "Hackney",
                  "Harrow",
                  "Hounslow",
                  "Islington",
                  "Sutton",
                  "Tower Hamlets",
                  "Wandsworth",
                  "Westminster")
regression_boroughs = c("Camden",
                        "Islington",
                        "Hackney",
                        #"Kensington and Chelsea",
                        "Westminster")
inner_boroughs = c("Camden",
                   "City of London",
                   "Greenwich",
                   "Hackney",
                   "Hammersmith and Fulham",
                   "Islington",
                   "Kensington and Chelsea",
                   "Lambeth",
                   "Lewisham",
                   "Southwark",
                   "Tower Hamlets",
                   "Wandsworth",
                   "Westminster")

borough_num <- data.frame(NUM = c(1:33), NAME = c("City of London", "Westminster", "Kensington and Chelsea", "Hammersmith and Fulham", "Wandsworth", "Lambeth", "Southwark", "Tower Hamlets", "Hackney", "Islington", "Camden", "Brent", "Ealing", "Hounslow", "Richmond upon Thames", "Kingston upon Thames", "Merton", "Sutton", "Croydon", "Bromley", "Lewisham", "Greenwich", "Bexley", "Havering", "Barking and Dagenham", "Redbridge", "Newham", "Waltham Forest", "Haringey", "Enfield", "Barnet", "Harrow", "Hillingdon"))

cand_num <- data.frame(CAND_NUM = c(1:9),
                       NAME = c("Camden",
                  "Hackney",
                  "Harrow",
                  "Hounslow",
                  "Islington",
                  "Sutton",
                  "Tower Hamlets",
                  "Wandsworth",
                  "Westminster"))
regression_num <- data.frame(REGRESS_NUM = c(1:4),
                             NAME = c("Hackney",
                                      "Islington",
                                      "Camden",
                                      "Westminster"
                                      #"Kensington and Chelsea"
                                      ))

# Add num to `borough_polygons`
borough_polygons <- borough_polygons %>%
  left_join(borough_num, by = "NAME")
borough_polygons <- borough_polygons %>%
  left_join(cand_num, by = "NAME")
borough_polygons <- borough_polygons %>%
  left_join(regression_num, by = "NAME")

borough_polygons <- borough_polygons %>%
  mutate(original_source = NAME %in% original_boroughs) %>%
  mutate(sampling_source = NAME %in% sampling_boroughs) %>%
  mutate(regression_source = NAME %in% regression_boroughs) %>%
  mutate(inner = NAME %in% inner_boroughs)
         
inner_london_polygons <- borough_polygons %>%
  filter(inner == TRUE)
sampling_borough_polygons <- borough_polygons %>%
  filter(sampling_source == TRUE)
regression_borough_polygons <- borough_polygons %>%
  filter(regression_source == TRUE)

# Displaying Polygons of Candidate Boroughs
library(ggspatial)
library(OpenStreetMap)
library(osmdata)
library(ggmap)
library(basemaps)
library(sf)
library(ggnewscale)
library(ggrepel)
```

```{r, fig.width = 6.5, fig.height = 4.5}
borough_polygons_draw <- st_transform(borough_polygons, crs = 3857)  # Web Mercator for compatibility
inner_london_polygons_draw <- st_transform(inner_london_polygons, crs = 3857)  # Web Mercator for compatibility
sampling_borough_polygons_draw <- st_transform(sampled_borough_polygons, crs = 3857)  # Web Mercator for compatibility

# Merge all borough polygons for a london polygon
london_polygon_draw <- st_union(borough_polygons_draw)
inner_london_draw <- st_union(inner_london_polygons_draw)

extent <- st_bbox(london_polygon_draw, crs = 3857)

get_maptypes()

# Create the plot
g_data_cand_all = ggplot() +
  # Add basemap
  basemap_gglayer(
    ext = london_polygon_draw,
    map_service = "carto",
    map_type = "light_no_labels",  # Or any basemap type you prefer
  ) +
  scale_fill_identity() + 
  # Add a new scale for the polygons
  new_scale_fill() +
  # Add borough polygons with independent fill
  geom_sf(data = borough_polygons_draw,
          aes(fill = original_source),
          inherit.aes = FALSE,
          alpha = 0.5,
          linewidth = 0.1) +
  # geom_sf(data = inner_london_draw,
  #         inherit.aes = FALSE,
  #         alpha = 0,
  #         linewidth = 0.5) +
  # Add labels for borough polygons
  geom_sf_text(data = (borough_polygons_draw),
                aes(label = NUM,
                geometry = geometry),
                stat = "sf_coordinates",
                inherit.aes = FALSE,
                # bold
                # fontface = "bold",
                min.segment.length = 0.5,
                segment.size = 0.1,
                box.padding = 0.1,
                direction = "y",
                size = 2) +
  
  # Define fill colors for borough polygons
  scale_fill_manual(values = c("TRUE" = "lightgreen", "FALSE" = "grey")) +
  
  # Add a scale bar
  annotation_scale(location = "bl",
                   pad_x = unit(.25, "cm"),
                   pad_y = unit(.25, "cm"),
                   width_hint = 0.2) +
  coord_sf(expand = FALSE) +
  # Add title and theme
  labs(title = "Candidate Boroughs for Analysis",
       legend = "Original Data Source") +
  theme_void() +
  theme(plot.margin = margin(0.1, 0.1, 0.1, 0.1, "cm"),
        plot.title = element_text(family = "Arial",
                                  size = 9,
                                  vjust = 3,
                                  hjust = 0.5),
        legend.position = "none")


#########


g_data_cand_inner = ggplot() +
  # Add basemap
  basemap_gglayer(
    ext = inner_london_draw,
    map_service = "carto",
    map_type = "light_no_labels",  # Or any basemap type you prefer
  ) +
  scale_fill_identity() + 
  # Add a new scale for the polygons
  new_scale_fill() +
  # Add borough polygons with independent fill
  geom_sf(data = borough_polygons_draw %>% filter(inner == TRUE),
          aes(fill = original_source),
          inherit.aes = FALSE,
          alpha = 0.4,
          linewidth = 0.1) +
  
  # Add labels for borough polygons
  geom_sf_text(data = (borough_polygons_draw %>% filter(inner == TRUE)),
                aes(label = NUM,
                geometry = geometry),
                stat = "sf_coordinates",
                inherit.aes = FALSE,
                # bold
                # fontface = "bold",
                min.segment.length = 0.7,
                segment.size = 0.1,
                box.padding = 0.1,
                direction = "y",
                size = 2) +
  
  # Define fill colors for borough polygons
  scale_fill_manual(values = c("TRUE" = "lightgreen", "FALSE" = "lightgrey")) +
  
  # Add a scale bar
  annotation_scale(location = "bl",
                   pad_x = unit(.25, "cm"),
                   pad_y = unit(.25, "cm"),
                   width_hint = 0.2) +
  coord_sf(expand = FALSE) +
  # Add title and theme
  labs(title = "Candidate Boroughs for Analysis (Inner London)",
       legend = "Original Data Source") +
  theme_void() +
  theme(plot.margin = margin(0.1, 0.1, 0.1, 0.1, "cm"),
        plot.title = element_text(family = "Arial",
                                  size = 9,
                                  vjust = 3,
                                  hjust = 0.5),
        legend.position = "none")

g_data_cand_all
g_data_cand_inner
ggsave("candidate_boroughs.png", plot = g_data_cand_all, width = 3.25, height = 3.25, dpi = 300)
ggsave("candidate_boroughs_inner.png", plot = g_data_cand_inner, width = 3.25, height = 3.25, dpi = 300)

library(patchwork)
library(gridExtra)
library(gt)
library(flextable)

g <- g_data_cand_all + g_data_cand_inner + plot_layout(ncol = 2)
ggsave("candidate_boroughs_combined.png", plot = g, width = 6.5, height = 3, dpi = 300)


# # Divide into two columns
# n <- nrow(borough_num)
# split_index <- ceiling(n / 2)
# 
# # Split the data into two equal parts
# split_index <- ceiling(n / 2)
# 
# # Pad the shorter column with NA if needed
# borough_split <- data.frame(
#   NUM_1 = borough_num$NUM[1:split_index],
#   NAME_1 = borough_num$NAME[1:split_index],
#   NUM_2 = c(borough_num$NUM[(split_index + 1):n], rep(NA, split_index - length((split_index + 1):n))),
#   NAME_2 = c(borough_num$NAME[(split_index + 1):n], rep(NA, split_index - length((split_index + 1):n)))
# )
# 
# # View the result
# print(borough_split)
# ??flextable
# # Convert the gt table into a graphical object
# g_data_cand_all + g_data_cand_inner + as_flextable.data.frame(borough_split)

```

# Example plots of  buffers combined with SVIs

```{r}
all_buffers

# Point borough example: Westminster
# buffers on bottom in red, alpha = 0.5
westminster_buffers_plot <- all_buffers %>% filter(borough == "Westminster")%>%
  st_transform(crs = 3857)
# parking spaces above in red, alpha = 1
westminster_clean_plot <- westminster_clean %>% st_transform(crs = 3857)
# SVIs above in blue, alpha = 1
westminster_svi_plot <- all_images_with_boroughs %>% filter(borough == "Westminster") %>%
  st_transform(crs = 3857)

# Set extent to a street in Westminster


ex_point_map <- ggplot() +
  # Add buffers
  geom_sf(data = westminster_buffers_plot,
          aes(fill = "red"),
          inherit.aes = FALSE,
          alpha = 0.5,
          linewidth = 0.1) +
  # Add parking spaces
  geom_sf(data = westminster_clean_plot,
          inherit.aes = FALSE,
          alpha = 1,
          color = "red",
          size = 0.5) +
  # Add SVIs
  geom_sf(data = westminster_svi_plot,
          inherit.aes = FALSE,
          alpha = 1,
          color = "blue",
          size = 0.5) +
  # Add a scale bar
  annotation_scale(location = "bl",
                   pad_x = unit(.25, "cm"),
                   pad_y = unit(.25, "cm"),
                   width_hint = 0.2) +
  coord_sf(expand = FALSE) +
  # Add title and theme
  labs(title = "Example Point Map",
       legend = "Original Data Source") +
  theme_void() +
  theme(plot.margin = margin(0.1, 0.1, 0.1, 0.1, "cm"),
        plot.title = element_text(family = "Arial",
                                  size = 9,
                                  vjust = 3,
                                  hjust = 0.5))

ex_point_map




# Westminster SVIs (simple map of SVIs in blue)




```