---
title: "borough_cleaner.rmd"
author: "Felix Bridgeman"
date: "2024-10-04"
output: html_document
---

This script imports ground truth parking data as shapefiles (either points, polylines, or polygons),
cleans them, and merges them into one clean file with which to conduct analysis.

Into ./data/clean/ this script saves the cleaned boroughs as shapefiles named [BOROUGH NAME]_clean.shp
as well as three merged files for each data type:
- joint_points_clean.shp
- joint_polygons_clean.shp
- joint_polylines_clean.shp

The cleaner also imports a shapefile of the PanoIDs of all SVIs
into an sf object called all_images, assigns them to a borough, cleans the sf object, and saves it as
"all_images_with_boroughs.shp" in the same directory.

INPUTS:
- raw borough shape files
- shapefile of all London borough polygons (from https://____, accessed ____)
- shapefile of all SVI PanoIDs (each PanoID is 1 point)

OUTPUTS:
- cleaned borough shapefiles
- merged shapefiles of all boroughs with points
- merged shapefiles of all boroughs with polygons
- merged shapefiles of all boroughs with polylines
- cleaned shapefile of all SVI PanoIDs with boroughs

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lwgeom)
library(sp)
library(sf)
library(ggplot2)
#setseed(123)
```

Import Point Data

32 Boroughs of London + City of London in Alphabetical Order:
- Barking & Dagenham
- Barnet
- Bexley
- Brent
- Bromley
- Camden (points)
- City of London (polygons)
- Croydon
- Ealing
- Enfield
- Greenwich
- Hackney (polygons)
- Hammersmith & Fulham
- Haringey
- Harrow (multipolygons)
- Havering
- Hillingdon
- Hounslow (polylines)
- Islington (polygons)
- Kensington and Chelsea
- Kingston upon Thames
- Lambeth
- Lewisham
- Merton
- Newham
- Redbridge
- Richmond upon Thames
- Southwark
- Sutton (multipolylines)
- Tower Hamlets (polylines)
- Waltham Forest
- Wandsworth (multipolygons)
- Westminster (points)


# Importing Data

Boroughs we have data on:
- Camden
- City of London
- Hackney
- Harrow
- Islington
- Sutton
- Tower Hamlets
- Wandsworth
- Westminster

## Borough (and Electoral Ward) Polygons

```{r}
# Import data
borough_polygons <- st_read(dsn = "../raw_london/On-street parking/On-street parking (Alex)", layer = "london_borough_onstreet")

```

## Point Boroughs

- Camden
- Westminster
- Kensington and Chelsea

```{r}
?read_sf
?st_read
# Import data
# Camden
camden <- st_read(dsn = "../raw_london/On-street parking/On-street parking (Alex)/Boroughs Parking data/Camden", layer = "Camden_NDVI")
# Westminster
westminster <- st_read(dsn = "../raw_london/On-street parking/On-street parking (Alex)/Boroughs Parking data/Westminster", layer = "Westminster_With NDVI")
# Kensington and Chelsea
kensington_and_chelsea <- st_read(dsn = "../raw_london/On-street parking/On-street parking (Alex)/Boroughs Parking data/Chelsea_Kensington/Buffered_NDVI.shp", layer = "Buffered_NDVI")

```

Camden:
Geodetic CRS = WGS 84
Westminster:
Projected CRS = OSGB36 / British National Grid

### Cleaning and merging point files

```{r}

# Check the structure of the data
head(camden, 2)
names(camden)
# parking.sp is parking spaces
head(westminster, 2)
# for westminster all parking spaces are just 1

# Equalise projections
camden_transformed <- st_transform(camden, crs = st_crs(borough_polygons))
ken_and_chel_transformed <- st_transform(kensington_and_chelsea, crs = st_crs(borough_polygons))
westminster_transformed <- st_transform(westminster, crs = st_crs(borough_polygons))

# Give IDs to Camden points according to ISO 3166-2:GB
camden_transformed$ID <- paste0("CMD_", seq_along(camden_transformed$geometry))
camden_transformed

# Give IDs to Kensington and Chelsea points according to ISO 3166-2:GB
# ken_and_chel_transformed$ID <- paste0("KEN_", seq_along(kensington_and_chelsea$geometry))
# ken_and_chel_transformed

# Standardize IDs for Westminster points
westminster_transformed$ID <- paste0("WSM_", seq_along(westminster$geometry))

# Make clean files for Camden and Westminster
# Camden: Keep ID, GSS_CODE, and Geometry
camden_clean <- camden_transformed %>%
  select(ID, GSS_CODE, Parking.Sp, geometry) %>%
  mutate(borough = "camden") %>%
  # Rename parking.sp to parking_spaces
  rename(parking_spaces = "Parking.Sp")

# # Kensington and Chelsea: Keep ID, GSS_CODE, and Geometry
# ken_and_chel_clean <- ken_and_chel_transformed %>%
#   select(ID, GSS_CODE, No_of_Bays, geometry) %>%
#   mutate(borough = "kensington_and_chelsea") %>%
#   # Rename parking.sp to parking_spaces
#   rename(parking_spaces = "No_of_Bays")

# Westminster: Keep ID, GSS_CODE, and Geometry
westminster_clean <- westminster_transformed %>%
  select(ID, GSS_CODE, geometry) %>%
  mutate(borough = "westminster") %>%
  # Add a column for parking_spaces
  mutate(parking_spaces = 1)

# Merge points
# ken_and_chel_clean
joint_points <- rbind(camden_clean, westminster_clean)

# Save the cleaned data to individual shapefiles
st_write(camden_clean, "./data/clean/individual_boroughs/camden_clean.shp", append = FALSE)

# # Save the cleaned Kensington and Chelsea data to a shapefile
# st_write(ken_and_chel_clean, "./data/clean/individual_boroughs/kensington_and_chelsea_clean.shp", append = FALSE)

# Save the cleaned Westminster data to a shapefile
st_write(westminster_clean, "./data/clean/individual_boroughs/westminster_clean.shp", append = FALSE)

# Filter out rows with empty geometry in joint_points
joint_points_clean <- joint_points %>%
  mutate(parking_spaces = as.numeric(parking_spaces))  %>% # make sure not char
  filter(!st_is_empty(geometry)) 
  
# Verify if there are still any empty geometries
sum(st_is_empty(joint_points_clean$geometry))  # This should return 0

# Save the cleaned joint_points dataset to a shapefile
st_write(joint_points_clean, "./data/clean/joint_points_clean.shp", append = FALSE)
```



## Polygon Boroughs

- City of London
- Hackney
- Harrow
- Islington
- Wandsworth

```{r}
# Import data
# City of London
city_of_london <- st_read(dsn = "../raw_london/On-street parking/On-street parking (Alex)/Boroughs Parking data/City of London", layer = "City of London_Merged")
# Number_of_ is the number of parking spaces

# Hackney
hackney <- st_read(dsn = "../raw_london/On-street parking/On-street parking (Alex)/Boroughs Parking data/Hackney", layer = "Hackney polygons")
# no_of_spac is the number of parking spaces

# Harrow
harrow <- st_read(dsn = "../raw_london/On-street parking/On-street parking (Alex)/Boroughs Parking data/Harrow_Parking_Bays[91]", layer = "All_Bays_New_Final", promote_to_multi = FALSE)
harrow <- st_cast(harrow, "POLYGON")
# NO_SPACES is the number of parking spaces

# Islington
islington <- st_read(dsn = "../raw_london/On-street parking/On-street parking (Alex)/Boroughs Parking data/Islington/Islington parking data.gpkg", layer = "Parking bays", promote_to_multi = FALSE)
islington <- st_cast(islington, "POLYGON")
# Spaces is the number of parking spaces

# Wandsworth
wandsworth <- st_read(dsn = "../raw_london/On-street parking/On-street parking (Alex)/Boroughs Parking data/Wandsworth", layer = "Parking Bays", promote_to_multi = FALSE)
wandsworth <- st_cast(wandsworth, "POLYGON")
# No number of parking spaces column

# Transform
city_of_london_transformed <- st_transform(city_of_london, crs = st_crs(borough_polygons))
hackney_transformed <- st_transform(hackney, crs = st_crs(borough_polygons))
harrow_transformed <- st_transform(harrow, crs = st_crs(borough_polygons)) 
islington_transformed <- st_transform(islington, crs = st_crs(borough_polygons))
wandsworth_transformed <- st_transform(wandsworth, crs = st_crs(borough_polygons))

# Give IDs
city_of_london_transformed$ID <- paste0("LND_", seq_along(city_of_london_transformed$geometry))
hackney_transformed$ID <- paste0("HCK_", seq_along(hackney_transformed$geometry))
harrow_transformed$ID <- paste0("HRW_", seq_along(harrow_transformed$geometry))
islington_transformed$ID <- paste0("ISL_", seq_along(islington_transformed$geometry))
wandsworth_transformed$ID <- paste0("WND_", seq_along(wandsworth_transformed$geometry))

# Clean
# City of London: Keep ID, geometry
city_of_london_clean <- city_of_london_transformed %>%
  select(ID, 
         Number_of_,
         geometry) %>%
  mutate(borough = "city_of_london") %>%
  rename(parking_spaces = "Number_of_")

# Hackney: Keep ID, geometry
hackney_clean <- hackney_transformed %>%
  select(ID,
         no_of_spac,
         geometry) %>%
  mutate(borough = "hackney") %>%
  rename(parking_spaces = "no_of_spac")

# Harrow: Keep ID, geometry
harrow_clean <- harrow_transformed %>%
  select(ID,
         NO_SPACES,
         geometry) %>%
  mutate(borough = "harrow") %>%
  rename(parking_spaces = "NO_SPACES")

# Islington: Keep ID, geometry
islington_clean <- islington_transformed %>%
  select(ID,
         #UniqueID,
         Spaces,
         geom) %>%
  # rename geom geometry
  rename(geometry = geom) %>%
  mutate(borough = "islington") %>%
  # Add a column for parking_spaces
  rename(parking_spaces = "Spaces") #%>%
  #rename(PMID = "UniqueID")

# Wandsworth: Keep ID, geometry
wandsworth_clean <- wandsworth_transformed %>%
  select(ID, geometry) %>%
  mutate(borough = "wandsworth") %>%
  # Add a column for parking_spaces
  mutate(parking_spaces = NA)


# merge
joint_polygons <- rbind(city_of_london_clean,
                        hackney_clean,
                        harrow_clean,
                        islington_clean,
                        wandsworth_clean) %>%
  mutate(parking_spaces = as.numeric(parking_spaces)) %>% # make sure not char
  # make valid to avoid problems down the line as seen during regression step
  st_make_valid(geometry)

# Filter out rows with empty geometry in joint_polygons
joint_polygons_clean <- joint_polygons %>%
  filter(!st_is_empty(geometry))

# Verify if there are still any empty geometries
sum(st_is_empty(joint_polygons_clean$geometry))  # This should return 0

# Save the cleaned data to individual shapefiles
st_write(city_of_london_clean, "./data/clean/individual_boroughs/city_of_london_clean.shp", append = FALSE)
st_write(hackney_clean, "./data/clean/individual_boroughs/hackney_clean.shp", append = FALSE)
st_write(harrow_clean, "./data/clean/individual_boroughs/harrow_clean.shp", append = FALSE)
st_write(islington_clean, "./data/clean/individual_boroughs/islington_clean.shp", append = FALSE)
st_write(wandsworth_clean, "./data/clean/individual_boroughs/wandsworth_clean.shp", append = FALSE)
# Save the cleaned joint_polygons dataset to a shapefile
st_write(joint_polygons_clean, "./data/clean/joint_polygons_clean.shp", append = FALSE)


```

## Polyline Boroughs

- Hounslow
- Sutton
- Tower Hamlets

```{r, fig.width = 20}
# Import data
# Hounslow
hounslow <- st_read(dsn = "../raw_london/On-street parking/On-street parking (Alex)/Boroughs Parking data/Hounslow new (GIS from FOI)", layer = "All Confirmed Static Orders_polyline")
hounslow <- st_zm(hounslow, drop = TRUE, what = "ZM")
hounslow$Order_type %>% unique()
# need to filter out the following Order_types:
waiting_filter = c("No loading at any time", "No loading", "School Keep Clear Mandatory", "Limited waiting", "Red Route Clearway AAT", "Red Route Loading Bay", "No waiting", "No waiting at any time", "Loading only")

# Sutton
sutton <- st_read(dsn = "../raw_london/On-street parking/On-street parking (Alex)/Boroughs Parking data/Sutton data", layer = "Sutton_onstreet_lines", promote_to_multi = FALSE)
sutton <- st_cast(sutton, "LINESTRING")
sutton$order_type %>% unique()
# need to filter out the following Order_types (capitalised)
waiting_filter2 = c("No Waiting", "No Waiting At Any Time", "No Loading", "No Loading At Any Time", "Loading Places", "No Stopping on School Entrance Marking", "Limited Waiting Bayes", "Crossing", "Bus Stop and Stands")

# Tower Hamlets
tower_hamlets <- st_read(dsn = "../raw_london/On-street parking/On-street parking (Alex)/Boroughs Parking data/Tower Hamlets", layer = "All Confirmed Static Orders 2021-06-29_lines")
tower_hamlets$Order_type %>% unique()

# need to filter out the following Order_types:
waiting_filter3 = c(
  "No Waiting At Any Time",
  "No Waiting",
  "No Loading At Any Time",
  "No Loading",
  "Limited Waiting",
  "Loading Place",
  "No Stopping on School Entrance Markings",
  "Bus Stop",
  "Bus Stand",
  "Pedestrian Crossing",
  "Keep Clear Entrance Marking")

# Transform
hounslow_transformed <- st_transform(hounslow, crs = st_crs(borough_polygons))
sutton_transformed <- st_transform(sutton, crs = st_crs(borough_polygons))
tower_hamlets_transformed <- st_transform(tower_hamlets, crs = st_crs(borough_polygons))

# Give IDs
hounslow_transformed$ID <- paste0("HNS_", seq_along(hounslow_transformed$geometry))
sutton_transformed$ID <- paste0("STN_", seq_along(sutton_transformed$geometry))
tower_hamlets_transformed$ID <- paste0("TWH_", seq_along(tower_hamlets_transformed$geometry))

# Clean
# Hounslow: Keep ID, geometry
hounslow_clean <- hounslow_transformed %>%
  # Filter Order_type 
  filter(!Order_type %in% waiting_filter) %>%
  mutate(length = st_length(geometry)) %>%
  mutate(parking_spaces = round(length / 4.8, 0)) %>%
  # as integer
  mutate(parking_spaces = as.integer(parking_spaces)) %>%
  select(ID, PMID, parking_spaces, geometry) %>%
  mutate(borough = "hounslow")

sum(hounslow_clean$parking_spaces)

# Sutton: Keep ID, geometry
sutton_clean <- sutton_transformed %>%
  filter(!order_type %in% waiting_filter2) %>%
  mutate(length = st_length(geometry)) %>%
  mutate(parking_spaces = round(length / 4.8, 0)) %>%
  # as integer
  mutate(parking_spaces = as.integer(parking_spaces)) %>%
  select(ID, pmid, parking_spaces, geometry) %>%
  mutate(borough = "sutton") %>%
  rename(PMID = "pmid")

# Tower Hamlets: Keep ID, geometry
tower_hamlets_clean <- tower_hamlets_transformed %>%
  filter(!Order_type %in% waiting_filter3) %>%
  mutate(length = st_length(geometry)) %>%
  mutate(parking_spaces = round(length / 4.8, 0)) %>%
  # as integer
  mutate(parking_spaces = as.integer(parking_spaces)) %>%
  select(ID, PMID, parking_spaces, geometry) %>%
  mutate(borough = "tower_hamlets")

# merge
joint_polylines <- rbind(hounslow_clean, sutton_clean, tower_hamlets_clean) %>%
  mutate(parking_spaces = as.numeric(parking_spaces)) # make sure not char

# Filter out rows with empty geometry in joint_polylines
joint_polylines_clean <- joint_polylines %>%
  filter(!st_is_empty(geometry))

# Verify if there are any empty geometries
sum(st_is_empty(joint_polylines_clean$geometry))  # This should return 0

# save the cleaned data to individual shapefiles
st_write(hounslow_clean, "./data/clean/individual_boroughs/hounslow_clean.shp", append = FALSE)
st_write(sutton_clean, "./data/clean/individual_boroughs/sutton_clean.shp", append = FALSE)
st_write(tower_hamlets_clean, "./data/clean/individual_boroughs/tower_hamlets_clean.shp", append = FALSE)
# Save the cleaned joint_polylines_clean dataset to a shapefile
st_write(joint_polylines_clean, "./data/clean/joint_polylines_clean.shp", append = FALSE)
joint_polylines_clean
```

## Photos from Google StreetView

```{r}
# Import data
all_images <- st_read(dsn = "../raw_london/images", layer = "imgDF_subset")

# How many panoids?
nrow(all_images)

# Transform projection
all_images_transformed <- st_transform(all_images, crs = st_crs(borough_polygons))

# Check CRS of both objects is ok
st_crs(borough_polygons) == st_crs(all_images_transformed)

# Assign boroughs to every panoid for reference later
all_images_with_boroughs <- st_join(all_images_transformed, borough_polygons["NAME"])

# rename the NAME column `borough`
all_images_with_boroughs <- all_images_with_boroughs %>%
  rename(borough = NAME)

# save all images with borough to a shapefile
st_write(all_images_with_boroughs, "./data/clean/all_images_with_boroughs.shp", append = FALSE)
```
